environmental_data_preperation

### 2018-09-19 src/environmental_data_preperation.Rmd
trying to extract amo data to the species dataset...
amo_sample added
amo timing correction

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
```{r pre-install packages, message=FALSE}
packages <- c("raster", "rgdal", "dplyr") 
source("../src/ipak.R")
ipak(packages)
```

@@

#if projectRaster woudl work properly...

@@

Now subset the dataset to start in 1998 (this is when the capelin dataset for the region starts)
```{r}
amoraw <- amoraw[amoraw$year >= 1998, ]
head(amoraw)
```

@@

ok lets try a different plot, lets try see which years were on average positive (above 0) and which were negative (below 0)

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
```{r pre-install packages, message=FALSE}
packages <- c("raster", "rgdal") 
source("../src/ipak.R")
ipak(packages)
```

@@

#if projectRaster would work properly...

@@

Now subset the dataset to start in 1997 (the capelin data starts in 1998, but you want some previous time period stuff)
```{r}
amoraw <- amoraw[amoraw$year >= 1997, ]
head(amoraw)
```

@@
